\textsf{Are large language models superhuman chemists?}

### 2024-10-28 src/tex/ms.tex
fix: correct automatic count link

\begin{table}[!h]
    \centering
    \caption{\textbf{Overview of sources of the curated questions}. The table provides an overview of the types of sources the questions have been curated from. Detailed sources are available in the source data on GitHub. Questions without source have been curated completely from scratch. Questions based on lecture notes or URL have been curated based on content presented in those resources. All questions have been rephrased, annotated, and reviewed before being added to the corpus. Note that the chemical preference questions are the main corpus of the semi-automatically generated group with 1001 questions of the total 1752.}
    \variable{output/sources_table.tex}
    \label{tab:sources}
\end{table}

>>>>

\begin{table}[!h]
    \centering
    \caption{\textbf{Overview of sources of the curated questions}. The table provides an overview of the types of sources the questions have been curated from. Detailed sources are available in the source data on GitHub. Questions without source have been curated completely from scratch. Questions based on lecture notes or URL have been curated based on content presented in those resources. All questions have been rephrased, annotated, and reviewed before being added to the corpus. Note that the chemical preference questions are the main corpus of the semi-automatically generated group with \variable{output/question_count_per_dir/json_file_counts_preference.txt} questions of the total \variable{output/automatically_generated.txt}.}
    \variable{output/sources_table.tex}
    \label{tab:sources}
\end{table}
